---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mixedup

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/m-clark/mixedup.svg?branch=master)](https://travis-ci.org/m-clark/mixedup)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/m-clark/mixedup?branch=master&svg=true)](https://ci.appveyor.com/project/m-clark/mixedup)
<!-- badges: end -->

Provides extended functionality for mixed models. The goal of mixedup is to solve little problems that slip through the cracks from the various packages, broom, and others.

## Installation

You can install mixedup from GitHub with `devtools`:

``` r
devtools::install_github('m-clark/mixedup')
```

## Example

Extract the random coefficients with their standard errors from `lme4` or `glmmTMB` objects.

```{r mods}
library(lme4)

lmer_1 <- lmer(Reaction ~ Days + (1 | Subject), data = sleepstudy)
lmer_2 <- lmer(Reaction ~ Days + (1 + Days| Subject), data = sleepstudy)

library(glmmTMB)

tmb_1 <- glmmTMB(Reaction ~ Days + (1 | Subject), data = sleepstudy)
tmb_2 <- glmmTMB(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)
```



```{r coefs}
library(mixedup)
extract_random_coef(lmer_1, which_re = 'Subject')


extract_random_coef(lmer_2, which_re = 'Subject')


extract_random_coef(tmb_1,  which_re = 'Subject')


extract_random_coef(tmb_2,  which_re = 'Subject')
```


Extract heterogeneous variances from nlme, which only reports the relative standard deviation values by default.

```{r nlme}
library(nlme)

model <- lme(
  distance ~ age + Sex, 
  data = Orthodont, 
  random = ~ 1|Subject,
  weights = varIdent(form = ~ 1 | Sex)
)

summary(model)

extract_nlme_variances(model)
```


## Other stuff

### Code of Conduct

Please note that the 'mixedup' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).

By contributing to this project, you agree to abide by its terms.

