---
title: "Miscellaneous Functions"
author: "Michael Clark"
date: <span style="font-style:normal;font-family:'Open Sans'">`r Sys.Date()`</span>
output:
  html_vignette:
    toc: true
    toc_depth: 3
    df_print: kable
vignette: >
  %\VignetteIndexEntry{Miscellaneous Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = T,
  message = F,
  warning = F,
  error = F,
  collapse = TRUE,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),
  dev = 'png',
  fig.align = 'center',
  out.width = '75%',
  fig.asp = .75,
  cache.rebuild = F,
  cache = F
)                                                    
```




## Intro

Miscellaneous functions are included to fill a need.

## Examples


### Find typical values

In many cases, predictions are made by holding the random effects to zero, which can be seen as the typical case. When the clusters carry substantive meaning, for example, school, country, or hospital, it might be of interest to note which are most 'typical', or at any other value relative to their peers.  This will work for any model to which `extract_random_effects` applies.

```{r typical}
library(lme4)

lmer_model <- lmer(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)

library(mixedup)

find_typical(lmer_model)  # closest RE to zero
find_typical(lmer_model, probs = c(.1, .9))
```


### Extract heterogeneous variances

For `nlme`, only models with `varIdent` have been tested.  For <span class="pack" style = "">glmmTMB</span>, this applies to models that use the <span class="func" style = "">diag</span> function in the formula.

```{r het-var}
library(nlme)

lme_1 <- lme(
  distance ~ scale(age) + Sex,
  data = Orthodont,
  random = ~ 1 | Subject,
  weights = varIdent(form = ~ 1 | Sex)
)

extract_het_var(lme_1)
```


May include <span class="pack" style = "">brms</span> at some point, but for
these, you can extract any parameters associated with sigma model for
distributional models using the `component` argument of the other standard
functions.


### Extract correlation structure

With some packages one can estimate the residual correlation structure.  Right now this works for <span class="pack" style = "">nlme</span>, <span class="pack" style = "">glmmTMB</span>, and <span class="pack" style = "">brms</span> objects.

```{r cor-struct}
base_model <-
  lme(Reaction ~ Days,
      random = ~ 1 + Days | Subject,
      data = sleepstudy)

lme_corSymm <-
  update(
    base_model,
    corr = corSymm(form = ~ 1 | Subject),
    data = dplyr::filter(sleepstudy, Days < 5)
  )

lme_corAR <-
  update(
    base_model,
    corr = corAR1(form = ~ Days),
    data = dplyr::filter(sleepstudy, Days < 5)
  )


extract_cor_structure(lme_corSymm)


extract_cor_structure(lme_corAR)
```


### Extract model data

Just a wrapper for `model.frame`.

```{r model-data}
extract_model_data(lmer_model)
```

