---
title: "Miscellaneous Functions"
author: "Michael Clark"
date: <span style="font-style:normal;font-family:'Open Sans'">`r Sys.Date()`</span>
output:
  html_vignette:
    toc: true
    toc_depth: 3
    df_print: kable
vignette: >
  %\VignetteIndexEntry{Miscellaneous Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = T,
  message = F,
  warning = F,
  error = F,
  collapse = TRUE,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),
  dev = 'png',
  fig.align = 'center',
  out.width = '75%',
  fig.asp = .75,
  cache.rebuild = F,
  cache = F
)                                                    
```




## Intro

Miscellaneous functions are included to fill a need.

## Examples


### Find typical values

In many cases, predictions are made by holding the random effects to zero, which can be seen as the typical case. When the clusters carry substantive meaning, for example, school, country, or hospital, it might be of interest to note which are most 'typical', or at any other value relative to their peers.

```{r typical}
library(lme4)

lmer_model <- lmer(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)

library(mixedup)

find_typical(lmer_model)  # closest RE to zero
find_typical(lmer_model, probs = c(.1, .9))
```


### Extract heterogeneous variances

For this form of model only.  May include glmmTMB and/or brms at some point, and possibly extend to extract the AR coefficient for AR1 models.

```{r het-var}
library(nlme)

lme_1 <- lme(
  distance ~ scale(age) + Sex,
  data = Orthodont,
  random = ~ 1 | Subject,
  weights = varIdent(form = ~ 1 | Sex)
)

extract_het_var(lme_1)
```


### Extract correlation structure

With some packages one can estimate the residual correlation structure.  Right now this only works for nlme objects.

```{r}
base_model <-
  lme(Reaction ~ Days,
      random = ~ 1 + Days | Subject,
      data = sleepstudy)

lme_corSymm <-
  update(
    base_model,
    corr = corSymm(form = ~ 1 | Subject),
    data = dplyr::filter(sleepstudy, Days < 5)
  )

lme_corAR <-
  update(
    base_model,
    corr = corAR1(form = ~ Days),
    data = dplyr::filter(sleepstudy, Days < 5)
  )


extract_cor_structure(lme_corSymm)


extract_cor_structure(lme_corAR)
```


### Extract model data

Just a wrapper for `model.frame`.

```{r model-data}
extract_model_data(lmer_model)
```

