---
title: "Summarize a Mixed Model"
author: "Michael Clark"
date: <span style="font-style:normal;font-family:'Open Sans'">`r Sys.Date()`</span>
output:
  html_vignette:
    toc: true
    toc_depth: 3
    df_print: kable
vignette: >
  %\VignetteIndexEntry{Summarize a Mixed Model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = T,
  message = T,
  warning = F,
  error = F,
  collapse = TRUE,
  comment = NA,
  R.options = list(width = 220),
  dev.args = list(bg = 'transparent'),
  dev = 'png',
  fig.align = 'center',
  out.width = '75%',
  fig.asp = .75,
  cache.rebuild = F,
  cache = F
)
```

```{r loadbrms, echo=FALSE}
brms_model <- mixedup:::brms_model
```


## Intro

This is pretty printing of results of a mixed model.  Correlations of random and fixed effects are turned off by default, as the focus of interest is usually the variance components and fixed effects themselves. 95% confidence intervals are provided by default.


## Examples

```{r mods, message=FALSE}
library(lme4)
library(glmmTMB)
library(nlme)
library(brms)
library(mgcv)


lmer_model <-
  lmer(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)

lme_model  <-
  lme(Reaction ~ Days, random = ~ 1 + Days | Subject, data = sleepstudy)

tmb_model  <-
  glmmTMB(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)

# brms_model <-
#   brm(Reaction ~ Days + (1 + Days | Subject), 
#       data = sleepstudy,
#       cores = 4,
#       refresh = -1,
#       verbose = FALSE
#   )

# this is akin to (1 | Subject) + (0 + Days | Subject) in lme4
mgcv_model <-
  gam(
    Reaction ~  Days +
      s(Subject, bs = 're') +
      s(Days, Subject, bs = 're'),
    data = lme4::sleepstudy,
    method = 'REML'
  )
```


```{r results}
library(mixedup)

summarize_model(lmer_model)


summarize_model(lme_model)


summarize_model(tmb_model)


summarize_model(brms_model)


summarize_model(mgcv_model)
```

## Options

```{r options}
summarize_model(
  lmer_model,
  ci = FALSE,
  cor_re = TRUE,
  cor_fe = TRUE,
  digits = 3
)


summarise_model(lmer_model, ci = FALSE)
```

## Get Convergence

Often a model estimated by <span class="pack" style = "">lme4</span> needs a bit of help for convergence.  At present this function only works for <span class="pack" style = "">lme4</span>, but then, that's mostly where you're going to have the problem.  This function will start with your current model and run it long enough to the point that if you still have problems, you probably *really* have data or model issues, and not just an estimation problem.  See [this](https://m-clark.github.io/posts/2020-03-16-convergence/) for details.


```{r convergence, warning=FALSE}
lmer_not_converged <- lmer(
  score ~ Machine + (1 + Machine | Worker),
  data = nlme::Machines
)

lmer_converged <- converge_it(lmer_not_converged) # final result is a converged model

summarize_model(lmer_converged, ci = FALSE)
```

